%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:aa
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete,
% awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
 
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{name }{surname}
\address{Position, place}
\mobile{mobile number}
%%% Social
\email{xxx.xx@mail.xxx.it}
\homepage{https://www.xxxxx.co}
%\github{posquit0}
%\linkedin{posquit0}
%%% Optionals
\position{MSc {\enskip\cdotp\enskip}Computer Science and Engineering}
%\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {$company_name$}
  { $company_location$\\
\\
}
\letterdate{\today}
\lettertitle{$job_title$}
\letteropening{Dear Sir/Madam}
\letterclosing{Sincerely,}
%\letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today }
  {Name Surname~~~·~~~Cover Letter}
  {}

\begin{document}
%%% Make a header for CV using personal data
\makecvheader
%%% Make a title for Cover Letter using letter data
\makelettertitle
%%% Write content for your cover letter
\begin{cvletter}
\cvparagraph{About Me}
I am a final year Master's degree student at xxxxxxxxxxx. My master's degree specialization consists of Machine Learning, Deep Learning, Computer Vision and Robotics. Currently, I am doing my thesis on deep learning, alongside am working as a Data Scientist Intern at xxxxxxxxxx. I will graduate in xxxxxxxxx so I am looking for an opportunity.
\cvparagraph{Current career}
I have several years of experience in image processing and computer vision. For example, in my bachelor's degree, I have done a project to xxxxxxxxxxxx. My bachelor thesis was about xxxxxxxxxx. My other projects also include robotics, internet of things, signal processing, machine learning, game design, Android applications, etc. Various topics and projects gave me a broad understanding of the different techniques and their importance.

Now I am working for xxxxxxxxxx intern, where we solve real-world problems by developing NLP, deep learning, and machine learning applications. These projects gave me more knowledge about natural language processing, data enrichment, data classification, Image analysis, computer vision, Docker, application deployment and testing.
\cvparagraph{Career goal}

I want to gain valuable experience in research in the field of AI and computer vision. This position will allow me to enrich my knowledge. $sentence$ $company_name$ will be an excellent opportunity for me to turn my goals into action. With a strong background in machine learning, deep learning, and computer vision, I would be confident to fulfill your requirements.
I am looking forward to your positive reply.

\end{cvletter}
%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
